\documentclass[12pt]{altacv}
\PassOptionsToPackage{dvipsnames}{xcolor}

\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm,footskip=2\baselineskip}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}

\definecolor{Purple}{HTML}{591B64}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{Purple}
\colorlet{accent}{Purple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\addbibresource{sample.bib}

\usepackage[colorlinks]{hyperref}
\hypersetup{
  colorlinks=true,
  urlcolor=Purple
}

\begin{document}

\name{Tyler Baum}
\tagline{Java, Python, \& Web Developer}
\personalinfo{
  \phone{(724) 762--2980}
  \email{\href{mailto:tyler.baum@protonmail.com}{\underline{tyler.baum@protonmail.com}}}
  \homepage{\href{https://augmentab.github.io}{\underline{augmentab.github.io}}}
  \linkedin{\href{https://linkedin.com/in/thebaum}{\underline{thebaum}}}
  \github{\href{https://github.com/AugmenTab}{\underline{AugmenTab}}}
}

\begin{fullwidth}
\makecvheader
\end{fullwidth}

\cvsection[page1sidebar]{Experience}

  \cvevent{Front-End Web Developer}{TreeForge, LLC}{Mar 2019 -- Present}{Albuquerque, NM}
  \begin{itemize}
  \item Designed and developed advertising and e-commerce sites for clients.
  \item Built an e-commerce site that saved the client over 300 hours in labor and increased revenue by 20\% in the first year.
  \item Linked sites to DatoCMS content management services to permit the clients to update site content and layout at their leisure.
  \item Managed contract workers in the creation of media assets and web designs.
  \end{itemize}

  \divider

  \cvevent{Java+Android Bootcamp Student}{CNM Ingenuity Deep Dive Coding}{Sep 2020 -- Dec 2020}{Albuquerque, NM}
  \begin{itemize}
  \item Attended Cohort 11 remotely for 40 hours each week and gained experience in working independently and as part of a team in a remote environment.
  \item Designed and built several Android apps and Java programs utilizing Spring, Hibernate, JavaFx, JUnit5, and SQL.
  \item Acted as project leader for AlbuQuirky, one of four final capstone projects.
  \end{itemize}

  \divider

  \cvevent{A.P. Cashier w/ Software Responsibilities}{Century Automotive Service Corporation}{Apr 2018 -- July 2020}{Albuquerque, NM}
  \begin{itemize}
  \item Designed, built, tested, and implemented custom software solutions to improve workflow and increase efficiency across multiple departments.
  \item Created processes that increased productivity by as much as 93\%.
  \item Managed relationships and processes for VIP accounts that were of high value to the company.
  \end{itemize}

\medskip

\end{document}
